Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-23 paper.tex
Back to abbrv bib style, since acm throws TeX warnings
Scale tables and figures to \linewidth
Tidy markup

\documentclass{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}
\usepackage{tabularx}
\usepackage{rotating}
\usepackage{tikz}
\usepackage{xspace}   %MF
\usepackage{enumitem} %MF

@@

\newcommand{\ie}{{i.e.,}\xspace}
\newcommand*\rot{\rotatebox{90}}

@@

\textbf{Timing and Deadlines:}
Timing is the most salient feature of real-time applications. Since their data
must be conveyed with real-time demands, they all have some concept of a
\emph{deadline}. Data that fails to present within the deadline is otherwise
useless.
% Deadlines may be short or long.
The `slack' in a deadline depends on the application. Interactive applications,
such as telephony, video conferencing, or telepresence, require low end-to-end
latency. Their deadlines for presenting the media, \ie playing the audio and
displaying the video frame, range from tens to a few hundred milliseconds.
Non-interactive application deadlines associated with broadcast and on-demand
programming are on the order of seconds.
% , such as broadcast TV, may have deadlines on the order of seconds,
% or even tens of seconds for on-demand programming.

@@

  \begin{tabularx}{\textwidth}{llll}

@@

\begin{figure}[t]
 \centering
 \includegraphics[scale=0.45]{figures/tcp-hollywood-fixed.pdf}
  \caption{TCP Hollywood architecture}
\label{diagram:tcp-hollywood}
\end{figure}

@@

%==================================================================================================
%\section{Acknowledgements}
%
% Acknowledge funding sources.
%
%==================================================================================================
\balance
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
% vim: set ts=2 sw=2 tw=75 et ai:

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}
\usepackage{tabularx}
\usepackage{rotating}
\usepackage{tikz}

@@

\newcommand*\rot{\rotatebox{90}}

@@

\textbf{Timing and Deadlines:}
Timing is the most salient feature of real-time applications. Since their data
must be conveyed with real-time demands, they all have some concept of a
\emph{deadline}. Data that fails to present within the deadline is otherwise
useless.
% Deadlines may be short or long.
The `slack' in a deadline depends on the application. Interactive applications,
such as telephony, video conferencing, or telepresence, require low end-to-end
latency. Their deadlines for presenting the media, i.e., playing the audio and
displaying the video frame, range from tens to a few hundred milliseconds.
Non-interactive application deadlines associated with broadcast and on-demand
programming are on the order of seconds.
% , such as broadcast TV, may have deadlines on the order of seconds,
% or even tens of seconds for on-demand programming.

@@

  \begin{tabularx}{\linewidth}{llll}

@@

\begin{figure}[t]
 \centering
  \includegraphics[width=\linewidth]{figures/tcp-hollywood-fixed.pdf}
  \caption{TCP Hollywood architecture}
\label{diagram:tcp-hollywood}
\end{figure}

@@

%==================================================================================================
%\section{Acknowledgements}
%
% Acknowledge funding sources.
%
%==================================================================================================
\balance
\bibliographystyle{abbrv}
\bibliography{paper}
\end{document}
% vim: set ts=2 sw=2 tw=75 et ai:
